A Survey on Ordered Binary Decision Diagrams

### 2015-09-14 paper.tex
Add descriptions of reference count and dead nodes

The first OBDD package containing kind of a garbage collection was the one
introduced by Brace, Bryant and Rudell~\cite{BRACE90}. The garbage collection was
based upon the reference counting technique, i.e. every node of the OBDD had a
reference count. This reference count represents two kinds of references, (1)
the number of other nodes and (2) the number of formulas referencing it, but does
not take references from the unique- and computed-table into account. \tbr

>>>>

The first OBDD package containing kind of a garbage collection was the one
introduced by Brace, Bryant and Rudell~\cite{BRACE90}. The garbage collection was
based upon the reference counting technique, i.e. every node of the OBDD had a
reference count. This reference count represents two kinds of references, (1)
the number of other nodes and (2) the number of formulas referencing it, but does
not take references from the unique- and computed-table into account.

Today, garbage collecion is a well-known topic. It is used to free up unnecessary
allocated or unused memory. To accomplish this, the garbage collection has to know
about which parts of the memory are \textit{dead} and thus can be freed. A node
of an OBDD is called \textit{dead} if the reference count of it is equal to zero.
The reference count of a node $x$ is decremented every time a corresponding
formula is freed. If the reference count of $x$ reaches zero, the reference counts
of $lo(x)$ and $hi(x)$ are decremented recursively.\tbr
